---
title: "Modeling of the large Miocene epithermal and porphyry gold deposits of Colombia"
subtitle: "Modified from Chiaradia & Caricchi, (2017) and Chiaradia (2020)"
author: "Felipe Velásquez, Juan Camilo Martinez, Alejandra Yepes Metaute"
date: "April 11, 2021"
output:
  html_document: default
  toc: true
  toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(rgl)
library(plot3D)

```

# Low flux modeling

## Data Input


# Time: 0 -5 Ma (Annen et al., 2006)
# Pressure: 1,5 - 9 Kbar (Annen et al., 2006)
# 5 mm/a of basaltic melt injection rate (Annen, 2009; Annen et al., 2006)
# 2 - 4% H2O in parent magma (Plank et al., 2013)  
# 0,2 - 1% H2O in crustal rocks (Chiaradia & Caricchi, 2017) 
# 10-100 of fluid-melt partition coefficient of gold (Simon et al., 2005) 
# 6 – 9 ppb of gold content in calc-alkaline magmas (Moss et al., 2001)
# Au Efficiency: Variable sensible


```{r inputs, echo = T}
#---------------------------------------------------------------------------------------
# Low flux:
#---------------------------------------------------------------------------------------

# Random variables as inputs.

n = 3000000         # Number of iterations
set.seed(123)     # Seeds

a = runif(n, 0, 5)                # a = time in Ma
bx = runif(n, 0.5, 1)             # bx = Au Efficiency (%)
b = runif(n, 2, 4)                # c= H2O in parent magma (wt.%)
c = runif(n, 0.2, 1)              # c = H2O in crustal rocks(wt.%)
d = runif(n, 1.5, 9)              # d = Pressure (kbars)
e = rep(5000, n)                  # e = magma rate (m/Ma)
g = runif(n, 6500, 8500)          # g = Disk radius (m)
j = runif(n, 10, 100)             # j = Kd Au
k = runif(n, 0.006, 0.009)        # K = Au total melt (ppm)

#---------------------------------------------------------------------------------------
# Data generating process:
#---------------------------------------------------------------------------------------
#Crustal Melt Calculations
#--------------------------------------------------------------------------------------

f = a*e                           # f= Magma rate time integrated (m/Ma)

hist(f, breaks = 75)
#---------------------------------------------------------------------------------------
#l= x crustal

l = -0.00000476*(a^{5}) + 0.00010012*(a^{4}) - 0.00087381*(a^{3}) + 0.00390394*(a^{2}) - 0.0087404*(a) + 0.00542933

hist(l, breaks = 75)

#---------------------------------------------------------------------------------------
#m= y crustal

m = 0.00025805*(a^{5}) - 0.00451301*(a^{4}) + 0.03096005*(a^{3}) -
  0.1047359*(a^{2}) + 0.17540876*(a) - 0.08277333

hist(m, breaks = 75)

#---------------------------------------------------------------------------------------
#nn= x crustal
nn = -0.00183672*(a^{5}) + 0.02924904*(a^{4}) - 0.1769496*(a^{3}) +
  0.50100047*(a^{2}) - 0.64552174*(a) + 0.2529533

hist(n, breaks = 75)

#---------------------------------------------------------------------------------------
#o= crustal melt fraction Annen 
o = l*(d^{2}) + m*(d) + nn

hist(o, breaks = 75)

#---------------------------------------------------------------------------------------
#p= crustal Melt fraction Annen logical test
p = 0
for(i in 1:n){
  if(o[i] < 0){
    p[i] = 0
  }
  else{
    p[i] = o[i]
  }
}

hist(p, breaks = 75)

#---------------------------------------------------------------------------------------
#q=crustal Melt fraction Annen logical test2 low
q = 0
for(i in 1:n){
  if((a[i] > 1) & (d[i] > 3)){
    q[i] = p[i]
  }
  else{
    q[i] = NA
  }
}

hist(q, breaks = 75)

#---------------------------------------------------------------------------------------
#r=crustal Melt fraction Annen logical test3
r = 0
for(i in 1:n){
  if((a[i] > 0.25) | (d[i] > 6)){
    r[i] = q[i]
  }
  else{
    r[i] = NA
  }
}

hist(r, breaks = 75)

#---------------------------------------------------------------------------------------
#s=volume of crustal melt fraction rate time integrated (m^3)
s = pi*(g^{2})*(f)*r 

hist(s, breaks = 75)
#---------------------------------------------------------------------------------------
#t= tons of crustal melt fraction time integrated
t = s*(2.6)

hist(t, breaks = 75)


#---------------------------------------------------------------------------------------
# u= crustal Melt percent Annen

u = r*100


#---------------------------------------------------------------------------------------
# Residual Melt Calculations
#---------------------------------------------------------------------------------------
#v= x residual
v = -0.00011309*(a^{6}) + 0.00186017*(a^{5}) - 0.01179089*(a^{4}) +
  0.03594339*(a^{3}) - 0.05316974*(a^{2}) + 0.03207473*(a) + 0.00018778

hist(v, breaks = 75)

#---------------------------------------------------------------------------------------
#w= y residual
w = 0.00120531*(a^{6}) - 0.01970898*(a^{5}) + 0.12379992*(a^{4}) -
  0.37149275*(a^{3}) + 0.53160183*(a^{2}) - 0.28832793*(a) - 0.00343741

hist(w, breaks = 75)

#---------------------------------------------------------------------------------------
# x= z residual
x = -0.00264884*(a^{6}) + 0.04269856*(a^{5}) - 0.26252652*(a^{4}) +
  0.7613096*(a^{3}) - 1.02505321*(a^{2}) + 0.52268727*(a) + 0.01527694

hist(x, breaks = 75)

#---------------------------------------------------------------------------------------
#y= residual Melt fraction Annen
y = v*(d^{2}) + w*(d) + x

hist(y, breaks = 75)
#---------------------------------------------------------------------------------------
#z= residual Melt fraction Annen logical test
z = 0

for(i in 1:n){
  if(y[i] < 0){
    z[i] = 0
  }
  else{
    z[i] = y[i]
  }
}

hist(z, breaks = 75)

#---------------------------------------------------------------------------------------
#aa= residual Melt fraction Annen logical test2
aa = 0
for(i in 1:n){
  if((a[i] > 0.5) & (d[i] > 3)){
    aa[i] = z[i]
  }
}

#--------------------------------------------------------------------------------------
#ab= volume of residual melt fracton time integrated

ab = pi*(g^{2})*(f)*aa

hist(ab, breaks = 75)

#---------------------------------------------------------------------------------------
# ac: tons of residual melt fraction time integrated

ac = 2.6*ab

hist(ac, breaks = 75)

#---------------------------------------------------------------------------------------
#ad= residual Melt percent Annen

ad = aa*100

hist(aa, breaks = 75)

#---------------------------------------------------------------------------------------
#Total Melt Calculations

#---------------------------------------------------------------------------------------
#ae= all_melt_percent_low
ae = u + ad

hist(ae, breaks = 75)

#---------------------------------------------------------------------------------------
#af= Total melt in tons

af = ac + t

#---------------------------------------------------------------------------------------
#ag= Volume km^3 total melt

ag = (af/2.5)/(10^{9})

hist(af, breaks = 75)

#---------------------------------------------------------------------------------------
#H2O Content Calculations in residual melt

#-------------------------------------------------------------------------------------------
#aj= H2O wt.% in residual melt

aj = 100*b*(ad^{-1})

#---------------------------------------------------------------------------------------
#al= r H2O

al =0.00000163*(d^{2})+0.00002024*(d)-0.00000718

hist(al, breaks = 75)

#---------------------------------------------------------------------------------------
#am= s H2O

am = -0.00088884*(d^{2})-0.0110706*(d)+0.00391827

hist(am, breaks = 75)

#---------------------------------------------------------------------------------------
# an: t H2O

an = 0.05908101*(d^{2}) + 1.91102201*(d) + 1.79358317

hist(an, breaks = 75)

#---------------------------------------------------------------------------------------
#ao: residual melt Annen logical test for H2O solubility (F=100-10%)

ao = 0

for(i in 1:n){
  if(is.na(ad[i]) == FALSE){
    if(ad[i] <= 10){
    ao[i] = 10
    }
  else if(ad[i] > 10){
    ao[i] = ad[i]
    }
  }
  else{
    ao[i] = NA
  }
}

hist(ao, breaks = 75)

#----------------------------------------------------------------------------------------
# ak: log test H2O wt% in residual melt
ak = 100*(b)*(ao^{-1})

hist(ak, breaks = 75)

#--------------------------------------------------------------------------------------
# ap: H2O solubility in melt (F =100-10 %)

ap = al*(ao^{2}) + am*ao +  an

hist(ap, breaks = 75)

#---------------------------------------------------------------------------------------------
# aq: H2O wt% in residual melt logical test 100-10% F range

aq = 0

for(i in 1:n){
  if((is.na(aj[i]) == FALSE) & (is.na(ap[i]) == FALSE)){
    if(aj[i] > ap[i]){
      aq[i] = ap[i]
    }
    else if(aj[i] <= ap[i]){
      aq[i] = aj[i]
    }
  }
  else{
    aq[i] = NA
  }
}


#---------------------------------------------------------------------------------------------
# ar: Excess residual H2O

ar = ak - ap

hist(ar, breaks = 75)

#--------------------------------------------------------------------------------------------
# at: Excess H2O residual (tons)

at = (ac*ar)/100

hist(at, breaks = 75)

#--------------------------------------------------------------------------------------------
# au: Log test excess residual H2O tons

au = 0

# =SI(AT3>0,AT3,0)

for(i in 1:n){
  if(is.na(at[i]) == FALSE){
    if(at[i] > 0){
      au[i] = at[i]
    }
    else{
      au[i] = 0
    }
  }
  else{
    au[i] = 0
  }
}

hist(au, breaks = 75)

#-------------------------------------------------------------------------------------------
# as: H2O residual (tons)

as  = (ac-au)*aq/100




```


## H2O Content Calcutation in Crustal Partial Melt


```{r pink, echo = T, eval = T}

#------------------------------------------------------------------------------
# av: H2O wt% in partial melt

av = 100*(c)*(u^{-1})

#------------------------------------------------------------------------
# aw : H2O solubility (wt.%) with Annen crustal melt % 

aw = (al*(u^{-2})) + (am*u) + an

#------------------------------------------------------------------------
# ax: H2O solubility (wt.%) with Annen crustal melt % logical test

ax = 0

for(i in 1:n){
  if((is.na(av[i]) == FALSE) & (is.na(aw[i]) == FALSE)){
    if(av[i] > aw[i]){
      ax[i] = av[i]
    }
    else if(av[i] <= aw[i]){
      ax[i] = aw[i]
    }
  }
  else{
    aq[i] = NA
  }
}

#------------------------------------------------------------------------
# AY: Excess H2O partial melt

ay = av - aw

hist(ay, breaks = 75)

#------------------------------------------------------------------------

# ba: Excess H2O crustal (tons)

ba = t*ay/100

#-------------------------------------------------------------------------
# BB: log test excess crustal H2O tons

# =SI(BA2>0,BA2,0)

bb = 0

for(i in 1:n){
  if((ba[i] > 0) & (is.na(ba[i])==FALSE)){
    bb[i] = ba[i]
  }
  else{
    bb[i] = 0
  }
}

hist(bb, breaks = 75)

#------------------------------------------------------------------------
#az = H2O crustal (tons)

az = (t-bb)*ax/100

#-------------------------------------------------------------------------

#ah= M res hydrous melt Ton

ah = ac-au+t-bb

#-------------------------------------------------------------------------

#ai=Volume Km^3 hydrous melt

ai = (ah/2.5)/1000000000

#-------------------------------------------------------------------------

```


## H2O Content calculations in total melt

```{r violeta, echo = T, eval = T}

#-------------------------------------------------------------------------
# bc: H2O total in melt (tons)

bc = as + az


#-------------------------------------------------------------------------
# bd: H2O% in hydrous melt

bd = bc/ah*100


#-------------------------------------------------------------------------
# be: exsolvable H2O tons

be = as + az


#-------------------------------------------------------------------------
# bf: Excess H2O total in melt (tons)

bf = at + ba

hist(bf, breaks = 75)


#-------------------------------------------------------------------------
# bg: Excess total H2O NEW log test

bg = au + bb

hist(bg, breaks = 75)

#-------------------------------------------------------------------------
# bh: M melt - excess H20 tons

bh = ac - au + t + bb

hist(bh, breaks = 75)


#-------------------------------------------------------------------------
# bi: % H2O excess

bi = af - bh

hist(bi, breaks = 75)

#-------------------------------------------------------------------------
# bj: Moles of excess H2O

bj = (bf*1000000)/(2*1.0079 + 15.99)

hist(bj, breaks = 75)


```

## GOLD ENDOWMENT CALCULATIONS 

```{r amarillo, echo = T, eval = T}

# bk: Au tot ton

bk = (k*af)/(10^{6})

hist(bk, breaks = 75)

#---------------------------------------------------------------------
# bl: Au ppm res melt

bl = bk/(j*bg + (af - bg))*1000000

hist(bl, breaks = 75)

#---------------------------------------------------------------------
# bm: Au ppm fluid

bm = j*bl

hist(bm, breaks = 75)

#---------------------------------------------------------------------
# bn: Au tot res melt Mt

bn = bl*(af-bg)/(1000000*1000000)

hist(bn, breaks = 75)

#---------------------------------------------------------------------
# bo: Au tot in excess fluid Mt

bo = bm*bg/(1000000*1000000)

hist(bo, breaks = 75)

#---------------------------------------------------------------------
# bp: 50% Au in excess fluid Mt

bp = bo/2

hist(bp, breaks = 75)

#---------------------------------------------------------------------
# bq: Au total Mt

bq = bn + bo

hist(bq, breaks = 75)

#---------------------------------------------------------------------
# br: Au tot ton

br = bl*ah/1000000

hist(br, breaks = 75)

#---------------------------------------------------------------------
# bs: Au tot ton

bs =br/(j*be+(ah-be))*1000000


#---------------------------------------------------------------------
# bt: Au fluid

bt = j*bs


#---------------------------------------------------------------------
# bu: Au tot res melt Mt

bu = bs*(ah-be)/(1000000*1000000)


#---------------------------------------------------------------------
# bv: Au tot in exsolvable fluid t

bv = bt*be/(1000000)

#---------------------------------------------------------------------
# bw: Au tot ton

bw =(bu+bv)*1000000


#---------------------------------------------------------------------
# by: Gold Endowment in  tons

by =bv*bx

hist(by, breaks = 75)


```

### Graphics:

```{r}


pipe_gold <- data.frame(cbind(by, ai, a, bx))


pipe_gold %>%
  ggplot(aes(x = by, y = ai, colour = a)) + 
  geom_point(aes(colour = a)) + 
  xlab("Gold Endowment (tons)") + 
  ylab("Volume hydrous melt (Km^3)") + 
  scale_colour_gradientn(colours = terrain.colors(n)) + 
  geom_vline(xintercept = 0, color = "red") + 
  geom_vline(xintercept = 1000, color = "red") 


pipe_gold %>%
  ggplot(aes(x=by)) +
  geom_histogram() +
  xlab("Gold endowment (tons)") +
  geom_vline(xintercept = 0, color = "red") +
  ylab("Frequency") + geom_vline(xintercept = 1000, color = "red") 



pipe_gold %>%
  ggplot(aes(x = by, y = ai, colour = bx)) +
  geom_point(aes(colour = bx)) + xlab("Gold Endowment (tons)") +
  ylab("Volume hydrous melt (Km^3)") +
   scale_colour_gradientn(colours = terrain.colors(n)) +
  geom_vline(xintercept = 0, color = "red") +
  geom_vline(xintercept = 1000, color = "red") 


 

```


# High flux

## Data Input


# Time: 40 Ka- 200 Ka (Annen, 2009)
# Pressure: 0,1-2 Kbar (Sanchez-Alfaro et al., 2016)
# 50 mm/a of basaltic melt injection rate (Annen, 2009; Annen et al., 2006)
# 2 - 4% H2O in parent magma (Plank et al., 2013)
# 0,2 - 1% H2O in crustal rocks (Chiaradia & Caricchi, 2017)
# 10-100 of fluid-melt partition coefficient of gold (Simon et al., 2005)
# 6 – 9 ppb of gold content in calc-alkaline magmas (Moss et al., 2001)
# Au Efficiency


```{r high, echo = T}
# High flux:

# # Random variables as inputs.

N = 2000000         # Number of iterations
set.seed(123)      # Seeds

A = runif(N, 40000, 200000)             # A Time in years
BD = runif(N, 1, 2)                     # BD = Au Efficiency (%)
B = runif(N, 2, 4)                      # B = H2O in parent magma (%)
C = runif(N, 0.2, 1)                    # C = H2O in crustal rocks (%)
D = runif(N, 0.3, 3)                    # D = Pressure (kbars)
E = rep(0.007, N)                       # E = Magma rate (Km3/Y)
FF = runif(N, 10, 100)                  # F = Kd Au
G = runif(N, 0.006, 0.009)              # G = Au total (ppm)
V = rep(27, N)                          #V= random dacite
#--------------------------------------------------------------------------------------

# Data generating process:

#------------------------------------------------

H = 0.00657*A-338.52065     #H = Volume of mobile magma Km^3

hist(H, breaks = 75)

#--------------------------------------------
#I= % mobile melt

I = runif(N, 0.61, 0.8)

#---------------------------------------------------
#J=Volume melt km3

J = H*I

#---------------------------------------------------
#K= Vol melt m3

K = J*1000000000

#-----------------------------------------------------
#L= Mass melt (tons)

L = K*2.5

#----------------------------------------------------
#M= Volume magma injected

M = 0.01566*A+31.01613

hist(M, breaks = 75)

#-----------------------------------------------------
#NN= Volume injection m^3

NN = M*1000000000

#------------------------------------------------------
#O= mass injection

O = NN*2.5

#-----------------------------------------------------
#P= % melt

P = L/O*100

hist(P, breaks = 75)

#-------------------------------------------------------
#Q= a Pressure high flux

Q = 0.0000000000212*P^{5} - 0.00000000358966*P^{4} + 0.0000002281984*P^{3} - 0.00000547616979*P^{2} + 0.00000241918607*P - 0.00368596666626

#------------------------------------------------------------
#R= b Pressure high flux

R = -0.00002265*P^{2} + 0.0063569*P + 0.46599948

#------------------------------------------------------------
#S= c Pressure high flux

S = 0.000026409*P^{2} - 0.014169134*P - 0.750571377

#--------------------------------------------------------------


#------------------------------------------------------------------
#W= residual melt Annen logical test for H2O solubility (F=100-10%)

W = I*V

hist(W, breaks = 75)

#-------------------------------------------------------------
#TT= P saturation

TT = Q*W^{2} + R*W + S

#-------------------------------------------------------------------
#U = Delta P

U = D - TT

hist(U, breaks = 75)

```
#H2O CONTENT CALCULATIONS IN TOTAL MELT

```{r high, echo = T}
#-----------------------------------------
#X= H2O wt% in residual melt

X = 100*B*30^{-1}

hist(X, breaks = 75)

#------------------------------------------
#Y= log test H2O wt% in residual melt

Y= 100*B*W^{-1}

#-----------------------------------------
#Z= a H2O high Flux

Z = 0.00000163*D^{2} +0.00002024*D -0.00000718

#--------------------------------------------
#AA= b H2O high flux

AA = -0.00088884*D^{2} - 0.0110706*D + 0.00391827

#--------------------------------------------
#AB= b H2O high flux

AB = 0.05908101*D^{2} + 1.91102201*D + 1.79358317

#--------------------------------------------------
#AC = H2O solubility in melt (F =100-10 %)

AC = Z*W^{2} + AA*W + AB

hist(AC, breaks = 75)

#-------------------------------------------------
#AD= H2O wt% in  melt logical test 100-10% F range

AD = 0

for(i in 1:N){
    if(X[i] > AC[i]){
      AD[i] = AC[i]
    }
    else if(X[i] <= AC[i]){
      AD[i] = X[i]
    }
  }


#----------------------------------------------------
#AE= Excess H2O %

AE = Y - AC


#-------------------------------------------------
#AG= Excess H2O  (tons)

AG = (K*2.5)*AE/100

#----------------------------------------------------
#AH = Excess H2O  (tons)

AH = 0

for(i in 1:N){
  if((AG[i] > 0) & (is.na(AG[i])==FALSE)){
    AH[i] = AG[i]
  }
  else{
    AH[i] = 0
  }
}



#----------------------------------------------------
#AI = new total hydrous melt

AI = (K*2.5)-AH

#---------------------------------------------------

#AF= H2O residual (tons)

AF = AI*AD/100

#---------------------------------------------------
#AJ= excess H2O ton

AJ = AE*L/100

#----------------------------------------------------
#AK = a Pressure

AK = 0.0000000000212*P^{5} - 0.00000000358966*P^{4} + 0.0000002281984*P^{3} - 0.00000547616979*P^{2} + 0.00000241918607*P - 0.00368596666626

#---------------------------------------------------
#AL = b Pressure

AL = -0.00002265*P^{2} + 0.0063569*P + 0.46599948

#---------------------------------------------------------
#AM = c Pressure

AM = 0.000026409*P^{2} - 0.014169134*P - 0.750571377

#------------------------------------------------------
#AP= H2O % in melt

AP = AF/AI*100

#-------------------------------------------------------
#AN = P saturation

AN = K*AP^{2} + AL*AP + AM

hist(AN, breaks = 75)

#----------------------------------------------------
#AO= Delta P


AO = D-AN

hist(AO, breaks = 75)
#------------------------------------------------------

```

#GOLD ENDOWMENT CALCULATIONS 

```{r high, echo = T}
#--------------------------------
#AQ= Au tot ton

AQ = G*L/1000000


#----------------------------
#AR= Au ppm res melt

AR = AQ/(FF*AG+(L-AG))*1000000

#------------------------------------
#AS= Au ppm fluid

AS =  FF*AR

hist(AS, breaks = 75)

#------------------------------------
#AT= Au tot res melt Mt

AT = AR*(L-AG)/(1000000*1000000)

#-----------------------------------
#AU=Au tot in excess fluid Mt

AU = AS*AG/(1000000*1000000)

#----------------------------------
#AV= 50% Au in excess fluid Mt

AV = AU/2

#-----------------------------------
#AW= Au tot Mt

AW = (AT+AU)

#-------------------------------
#BF=M res hydrous  melt (ton)

BF = AI

hist(BF, breaks = 75)

#----------------------------------
#BG=% H2O in hydrous melt

BG = Y

hist(BG, breaks = 75)

#--------------------------------
#BH=Exsolvable H2O (ton)

BH = BG*BF/100

#----------------------------------
#BI=Volume hidrous melt Km3

BI = AI/(2.3*1000000000)

#----------------------------------
#AX=Au tot ton

AX = AR*BF/1000000

hist(AX, breaks = 75)

#-----------------------------------
#AY= Au res melt

AY = AX/(FF*BH+(BF-BH))*1000000

#----------------------------------
#AZ=Au fluid

AZ = FF*AY

#---------------------------------------
#BA=Au tot res melt Mt

BA = AY*(BF-BH)/(1000000*1000000)

hist(BA, breaks = 75)

#-----------------------------------------
#BB=Au tot in exsolvable fluid t

BB = AZ*AG/(1000000)

hist(BB, breaks = 75)

#---------------------------------
#BC=Au tot t

BC = (BA+BB)*1000000

#-----------------------------------
#BE=Gold Endowments

BE = BB*BD

hist(BE, breaks = 75)


```


### Graphics:

```{r high, echo = T}

require(cowplot)
   
pipe_gold <- data.frame(cbind(BE, BI, A, D))



pipe_gold %>%
  ggplot(aes(x = BE, y = BI, colour = A)) +
  geom_point(aes(colour = A)) + xlab("Gold Endowment (tons)") +
  ylab("Volume hydrous melt (Km^3)") +
   scale_colour_gradientn(colours = terrain.colors(n)) +
  geom_vline(xintercept = 0, color = "red") +
  geom_vline(xintercept = 1000, color = "red") 



pipe_gold %>%
  ggplot(aes(x=BE)) +
  geom_histogram() +
  xlab("Gold endowment (tons)") +
  geom_vline(xintercept = 0, color = "red") +
  ylab("Frequency") + geom_vline(xintercept = 1000, color = "red") 



pipe_gold %>%
  ggplot(aes(x = BE, y = BI, colour = D)) +
  geom_point(aes(colour = D)) + xlab("Gold Endowment (tons)") +
  ylab("Volume hydrous melt (Km^3)") +
   scale_colour_gradientn(colours = terrain.colors(n)) +
  geom_vline(xintercept = 0, color = "red") +
  geom_vline(xintercept = 1000, color = "red") 



```


# Bibliography

# 1-Annen, C. (2009). From plutons to magma chambers: Thermal constraints on the accumulation of eruptible silicic magma in the upper crust. Earth and Planetary Science Letters, 284(3–4), 409–416. https://doi.org/10.1016/j.epsl.2009.05.006

# 2-Annen, C., Blundy, J. D., & Sparks, R. S. J. (2006). The genesis of intermediate and silicic magmas in deep crustal hot zones. Journal of Petrology, 47(3), 505–539. https://doi.org/10.1093/petrology/egi084

# 3-Chiaradia, M., & Caricchi, L. (2017). Stochastic modelling of deep magmatic controls on porphyry copper deposit endowment. Scientific Reports, 7(January 2016), 1–11. https://doi.org/10.1038/srep44523

# 4-Chiaradia, M. (2020). Gold endowments of porphyry deposits controlled by precipitation efficiency. Nature Communications, (2020) 11:248, 1-10. https://doi.org/10.1038/s41467-019-14113-1

# 5-Moss, R., Scott, S. D., & Binns, A. R. A. (2001). Gold content of eastern Manus basin volcanic rocks: Implications for enrichment in associated hydrothermal precipitates. Economic Geology, 96(1), 91–107. https://doi.org/10.2113/gsecongeo.96.1.91

# 6-Plank, T., Kelley, K. A., Zimmer, M. M., Hauri, E. H., & Wallace, P. J. (2013). Why do mafic arc magmas contain 4wt% water on average? Earth and Planetary Science Letters, 364, 168–179. https://doi.org/10.1016/j.epsl.2012.11.044

# 7-Sanchez-Alfaro, P., Reich, M., Driesner, T., Cembrano, J., Arancibia, G., Pérez-Flores, P., Heinrich, C. A., Rowland, J., Tardani, D., Lange, D., & Campos, E. (2016). The optimal windows for seismically-enhanced gold precipitation in the epithermal environment. Ore Geology Reviews, 79, 463–473. https://doi.org/10.1016/j.oregeorev.2016.06.005

# 8-Simon, A. C., Frank, M. R., Pettke, T., Candela, P. A., Piccoli, P. M., & Heinrich, C. A. (2005). Gold partitioning in melt-vapor-brine systems. Geochimica et Cosmochimica Acta, 69(13), 3321–3335. https://doi.org/10.1016/j.gca.2005.01.028


